Digital History in Finland, 1488-1828

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

@@

After initial preprocessing, we had `r nrow(subset(df0, catalog == "Fennica"))` and `r nrow(subset(df0, catalog == "Kungliga"))` documents in Fennica and Kungliga, respectively between the years `r min(df0$publication_year)`-`r max(df0$publication_year)`.

>>>>

fenraw <- readRDS("df.raw.Rds")
kunraw <- readRDS("../../../kungliga/antagomir/df.raw.Rds")

@@

The raw data contains metadata `r nrow(fenraw)` and `r nrow(kunraw)` documents in Fennica and Kungliga, respectively. After initial preprocessing and limiting the analysis between the years `r min(df0$publication_year)`-`r max(df0$publication_year)`, we had `r nrow(subset(df0, catalog == "Fennica"))` and `r nrow(subset(df0, catalog == "Kungliga"))` documents for Fennica and Kungliga, respectively.
